NN_Accel_Heading

### 2024-03-07 Fish Data Analysis/NN_Accel_Heading.qmd
Save before I make it all radians for sanity

fish_data_nn <- fish_comp_data_combo %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    filter(row_n == 1) %>%
                                    ungroup() %>%
                                    mutate(Angle_Rads = deg2rad(Angle),
                                           Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS))

nn_heading_sum <- fish_data_nn %>% mutate(angle_bins = round_any(Angle_Rads,pi/4)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

@@

heading_ps_angle_base <- lm(Fish1_Yaw_Heading_PS ~ 1, data = fish_data_nn %>% filter(Flow == "Still Water"))

heading_ps_angle_step <- stepAIC(heading_ps_angle_base, 
                                   list(upper = ~ (Angle_Rads+cos(Angle_Rads)+sin(Angle_Rads))*Ablation*Darkness, lower = ~1), 
                                   direction = "both",
                                   trace = F)

@@

ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
       aes(x = Angle_Rads, y = Fish1_Yaw_Heading_PS, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(alpha = 0.1)+
  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
  geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
  theme_classic() +
  #ylim(-5,5)+
  xlab("direction of neighbour (rad)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
  labs(color = "Sensory Conditions")

ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = mean_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  geom_line(alpha = 0.75) +
  #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
  theme_classic() +
  xlab("direction of neighbour (rad)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
  labs(color = "Sensory Conditions")

>>>>

fish_data_nn <- fish_comp_data_combo %>% group_by(Fish1,Tailbeat_Num,Data_ID) %>%
                                    mutate(nndDistance = min(Distance, na.rm = TRUE),
                                           nndDistance = ifelse(is.infinite(nndDistance), NA, nndDistance),
                                           all_nas = all(is.na(nndDistance))) %>%
                                    filter(Distance == nndDistance | all_nas) %>%
                                    mutate(row_n = row_number()) %>%
                                    filter(row_n == 1) %>%
                                    ungroup() %>%
                                    mutate(Angle_Rads = deg2rad(Angle),
                                           Fish1_Yaw_Heading_PS = deg2rad(Fish1_Yaw_Heading_PS)) %>%
                                    filter(Distance <= 2)

nn_heading_sum <- fish_data_nn %>% mutate(angle_bins = round_any(Angle_Rads,pi/8)) %>%
                                                group_by(angle_bins,Flow,Ablation,Darkness,Flow_Ablation_Darkness) %>%
                                                summarise(mean_turn = mean(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          sd_turn = sd(Fish1_Yaw_Heading_PS, na.rm = T),
                                                          n = n()) %>%
                                                ungroup() %>%
                                                na.omit()

@@

fish_data_nn_model <- fish_data_nn %>% filter(Flow == "Still Water") %>% 
                                       mutate(AblationCat = ifelse(Ablation == "Ablated",1,0),
                                              DarknessCat = ifelse(Darkness == "Dark",1,0))

heading_ps_angle_base <- lm(Fish1_Yaw_Heading_PS ~ 1, data = fish_data_nn_model)

heading_ps_angle_step <- stepAIC(heading_ps_angle_base,
                                   list(upper = ~ ((cos(Angle_Rads)+sin(Angle_Rads))*Ablation*Darkness), lower = ~1),
                                   direction = "both",
                                   trace = F)

@@

tester_model <- lm(Fish1_Yaw_Heading_PS ~ sin(Angle_Rads)*Ablation*Darkness, data = fish_data_nn_model) 
Anova(tester_model)

ggplot(fish_data_nn %>% filter(Flow == "Still Water"),
       aes(x = Angle_Rads, y = Fish1_Yaw_Heading_PS, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point(alpha = 0.1)+
  facet_wrap(~ interaction(Ablation, Darkness, sep =", ")) +
  #geom_smooth(se = F)+
  geom_smooth(se = F, method = glm, formula = y ~ 1)+
  #geom_line(aes(y = predict(heading_ps_angle_step)), size = 1)+
  theme_classic() +
  #ylim(-5,5)+
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle (rad/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  labs(color = "Sensory Conditions")

ggplot(nn_heading_sum %>% filter(Flow == "Still Water"),
       aes(x = angle_bins, y = rad2deg(mean_turn), color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_smooth(se = F)+
  #geom_line(aes(y = sin_pred)) +
  #geom_line(alpha = 0.75) +
  #geom_smooth(se = F, method = glm, formula = y ~ sin(x))+
  geom_line(aes(y = rad2deg(predict(heading_ps_angle_step,
                    newdata = nn_heading_sum %>% filter(Flow == "Still Water") %>% mutate(Angle_Rads = angle_bins)))), size = 1)+
  theme_classic() +
  #ylim(-0.6,0.6)+
  xlab("direction of neighbour (degrees)") +
  ylab("focal fish turning angle (degrees/sec)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
                     labels = rad2deg(unique(nn_heading_sum$angle_bins))) +
  # scale_x_continuous(breaks = unique(nn_heading_sum$angle_bins),
  #                    labels = c("-π","-3π/4","-π/2","-π/4","0","π/4","π/2","3π/4","π"))+
  labs(color = "Sensory Conditions")
